Who does big team science?

### 2022-06-03 03.data_analysis.Rmd
pushing old updates

```{r}
library(dplyr)
library(bib2df)
library(rio)
library(tidyr)
library(ggplot2)
library(nlme)
library(RColorBrewer)
current_year <- 2022
#### fix sau chins paper #### https://osf.io/gq92w/ 
```

@@

@@

# variance model 
variance_df <- merged_df %>% 
  group_by(TITLE) %>% 
  summarize(year = mean(YEAR), 
            var_o_career_1_pub = sd(o_career_1_pub, na.rm = T),
            var_s_career_1_pub = sd(s_career_1_pub, na.rm = T), 
            var_o_career_1_degree = sd(o_career_1_degree, na.rm = T))

@@

```{r}
# what do these people publish overall
table(o_works$our_type)

# publication rates ORCID
ggplot(merged_df, aes(graph_year, o_total_pub)) + 
  geom_violin() + 
  geom_jitter(height = 0, width = 0.1) + 
  theme_classic() + 
  ylab("Total Publications (ORCID)") + 
  xlab("Year of Publication")

### will ask KD about this one ###
o_total_model <- lme(o_total_pub ~ YEAR,
                      data = merged_df,
                      na.action = "na.omit",
                      random = ~1|JOURNAL)

summary(o_total_model)

# publication rates scholar
ggplot(merged_df, aes(graph_year, s_total_pub)) + 
  geom_violin() + 
  geom_jitter(height = 0, width = 0.1) + 
  theme_classic() + 
  ylab("Total Publications (Scholar)") + 
  xlab("Year of Publication")

### will ask KD about this one ###
s_total_model <- lme(s_total_pub ~ YEAR,
                      data = merged_df,
                      na.action = "na.omit",
                      random = ~1|JOURNAL)

summary(s_total_model)

# h index rates scholar
ggplot(merged_df, aes(graph_year, h_index)) + 
  geom_violin() + 
  geom_jitter(height = 0, width = 0.1) + 
  theme_classic() + 
  ylab("H Index") + 
  xlab("Year of Publication")

### will ask KD about this one ###
h_index_model <- lme(h_index ~ YEAR,
                      data = merged_df,
                      na.action = "na.omit",
                      random = ~1|JOURNAL)

summary(h_index_model)

# i 10 rates scholar
ggplot(merged_df, aes(graph_year, i10_index)) + 
  geom_violin() + 
  geom_jitter(height = 0, width = 0.1) + 
  theme_classic() + 
  ylab("H Index") + 
  xlab("Year of Publication")

### will ask KD about this one ###
i_index_model <- lme(i10_index ~ YEAR,
                      data = merged_df,
                      na.action = "na.omit",
                      random = ~1|JOURNAL)

summary(i_index_model)
```

### More Authors Over Time?

```{r}
author_count <- 
  merged_df %>% 
  group_by(TITLE) %>% 
  summarize(author_count = n(),
            year = mean(YEAR))

cor(author_count$author_count, author_count$year)

ggplot(author_count, aes(factor(year), author_count)) +
  theme_classic() + 
  geom_point() + 
  xlab("Year of Publication") + 
  ylab("Number of Authors")
```

### Where are Authors?

```{r}
# where did they get their degree
merged_df %>% 
  filter(!duplicated(ORCID)) %>% 
  count(education_summary_organization_address_country)

table(merged_df$education_summary_organization_address_country,
      merged_df$YEAR)

# how many different countries does each year have and is that getting bigger

# where do they work
merged_df %>% 
  filter(!duplicated(ORCID)) %>% 
  count(employment_summary_organization_address_country)

table(merged_df$employment_summary_organization_address_country,
      merged_df$YEAR)
```

@@

```{r}
# un regions grouping do this above 
# grab first X authors and last author
# and the last one for 10 - 49
num_grab <- 3

@@

# group into UN regions 
```

- credit contributions ? are we using de-weirding by using those people for translation and data collection only 
  - grab major roles and see what the diversity is 
  - look at the first 10 people and the last author 
  - maybe compare to the other 10 groups (1/3rd, middle, last 1/3rd)

## Journal Analysis

### Which Journals

### Article Topics Global Type

- hand coded information on what the articles are about 
- Types of big team research (social, cognitive) using keywords

```{r}
# table of hand coded type
```

### Article Types Over Time

- Over time: are things becoming more varied
- are the publications more varied over time

```{r}
# table of hand coded type by year 
```

>>>>

```{r}
library(dplyr)
library(bib2df)
library(rio)
library(tidyr)
library(ggplot2)
library(nlme)
library(RColorBrewer)
library(countrycode)
current_year <- 2022
#### fix sau chins paper #### https://osf.io/gq92w/ 
```

@@

```{r}
# total count of authors
author_count <- 
  merged_df %>% 
  group_by(TITLE) %>% 
  summarize(author_count = n(),
            year = mean(YEAR))
```

@@

# variance model 
variance_df <- merged_df %>% 
  group_by(TITLE) %>% 
  summarize(year = mean(YEAR), 
            var_o_career_1_pub = sd(o_career_1_pub, na.rm = T),
            var_s_career_1_pub = sd(s_career_1_pub, na.rm = T), 
            var_o_career_1_degree = sd(o_career_1_degree, na.rm = T),
            var_o_total = sd(o_total_pub, na.rm = T), 
            var_s_total = sd(s_total_pub, na.rm = T))

@@

```{r}
publication_overall <- as.data.frame(table(o_works$our_type)) %>% 
  arrange(desc(Freq)) %>% 
  mutate(Percent = Freq / sum(Freq) * 100)
```

### Publication Metrics

```{r}
# total pubs orcid ----

# graph 
o_total_graph <- ggplot(merged_df, aes(graph_year, o_total_pub)) + 
  geom_violin() + 
  geom_jitter(height = 0, width = 0.2, aes(color = TITLE_color)) + 
  theme_classic() + 
  ylab("Total Number of Publications (ORCID)") + 
  xlab("Year of Publication") +
  theme(legend.position="none")

# year model slope 
o_total_model <- lme(o_total_pub ~ YEAR,
                      data = merged_df,
                      na.action = "na.omit",
                      random = ~1|scholar)

# variance  model 
var_o_total_model <- lm(var_o_total ~ year, 
                          data = variance_df,
                          na.action = "na.omit")
```

```{r}
# total pubs scholar ----

# graph 
s_total_graph <- ggplot(merged_df, aes(graph_year, s_total_pub)) + 
  geom_violin() + 
  geom_jitter(height = 0, width = 0.2, aes(color = TITLE_color)) + 
  theme_classic() + 
  ylab("Total Number of Publications (ORCID)") + 
  xlab("Year of Publication") +
  theme(legend.position="none")

# year model slope 
s_total_model <- lme(s_total_pub ~ YEAR,
                      data = merged_df,
                      na.action = "na.omit",
                      random = ~1|scholar)

# variance  model 
var_s_total_model <- lm(var_s_total ~ year, 
                          data = variance_df,
                          na.action = "na.omit")
```

### Geopolitical Regions

```{r}
# map of degree representation

# map of last job representation

# how many different countries does each year have and is that getting bigger
country_summary <- merged_df %>% 
  group_by(TITLE) %>% 
  summarize(year = mean(YEAR), 
            edu_country = length(table(education_summary_organization_address_country)),
            job_country = length(table(employment_summary_organization_address_country)))

# totals by edu
edu_country_model <- lm(edu_country ~ year, 
                          data = country_summary,
                          na.action = "na.omit")

# totals by job
job_country_model <- lm(job_country ~ year, 
                          data = country_summary,
                          na.action = "na.omit")

@@

```{r}
# transform to un regions
merged_df$un_region_ed <- 
  countrycode(
    sourcevar = merged_df$education_summary_organization_address_country,
    origin = "iso2c",
    destination = "un.regionsub.name")

merged_df$un_region_job <- 
  countrycode(
    sourcevar = merged_df$employment_summary_organization_address_country,
    origin = "iso2c",
    destination = "un.regionsub.name")

# grab first X authors and last author
# and the last one for 10 - 49
num_grab <- 3

@@

- grab the first X authors and the last authors
- compare to random samples of other authors of the same size chunk 
- calculate the probability of having *anyone* from a un region in that chunk
- make two graphs one of probability of being in the first group, one of probability of being in second group

### 2022-06-03 04.manuscript.Rmd
pushing old updates

**_Types of Publications_**. We will summarize the coded types of publications for individuals and demonstrate the changes in types of publications over time visually. We will comment if more "open" type publications appear to be published, such as data-sets, preprints, and software.

**_Publication Metrics_**. 
- means and SDs for i10 and hindex information, and number of publications 
- same analyses as career length - slope of number of publications and variance of number of publications 
- slope up means people who are publishing more are more represented in the researchers
- slope down means more people with less publications
- answer are we giving opportunities to people who need the bean counting

@@

**_Education_**. Overall, individuals **at the time of publication** in big team science publications are  `r education_overall$Var1[1]` (`r format(education_overall$Percent[1], nsmall = 1, digits = 1)`%), `r education_overall$Var1[2]` (`r format(education_overall$Percent[2], nsmall = 1, digits = 1)`%), and`r education_overall$Var1[3]` (`r format(education_overall$Percent[3], nsmall = 1, digits = 1)`%). Here, we will talk about the figure below and how the trends occur across time.

@@

**_Types of Publications_**. 
- print out overall
- print out over time 
- open science question

**_Publication Metrics_**. 
- means and SDs for i10 and hindex information, and number of publications 
- same analyses as career length - slope of number of publications and variance of number of publications 
- slope up means people who are publishing more are more represented in the researchers
- slope down means more people with less publications
- answer are we giving opportunities to people who need the bean counting

@@

>>>>

**_Types of Publications_**. We will summarize the coded types of publications for individuals.

**_Publication Metrics_**. We will report descriptive statistics on the total number of publications, i10 index, and h-index for individuals overall. Next, we will use the same analyses described in the career length section to analyze trends over time. An increasing slope over time indicates that individuals who are publishing more are more represented in big-team science over time (i.e., increasing numbers of scholars with higher publication rates), while a negative slope indicates more researchers with less publications. A positive slope for variance indicates increasing variance over time (i.e., more diversity in the individual publication rates), while a negative slope would indicate less diversity in researchers over time. While publication rates do not represent value as a researcher, they are often used in hiring and promotion decisions, and we will use this variable as a proxy to gauge the diversity in scholars represented in big teams.

@@

**_Education_**. Overall, individuals **at the time of publication** in big team science publications are  `r education_overall$Var1[1]` (`r format(education_overall$Percent[1], nsmall = 1, digits = 1)`%), `r education_overall$Var1[2]` (`r format(education_overall$Percent[2], nsmall = 1, digits = 1)`%), and `r education_overall$Var1[3]` (`r format(education_overall$Percent[3], nsmall = 1, digits = 1)`%). Here, we will talk about the figure below and how the trends occur across time.

@@

**_Types of Publications_**. In general, the most common type of publication was `r publication_overall$Var1[1]` (`r format(publication_overall$Percent[1], nsmall = 1, digits = 1)`%), followed by `r publication_overall$Var1[2]` (`r format(publication_overall$Percent[2], nsmall = 1, digits = 1)`%), and smaller categories for `r publication_overall$Var1[3]` (`r format(publication_overall$Percent[3], nsmall = 1, digits = 1)`%), `r publication_overall$Var1[4]` (`r format(publication_overall$Percent[4], nsmall = 1, digits = 1)`%), `r publication_overall$Var1[5]` (`r format(publication_overall$Percent[5], nsmall = 1, digits = 1)`%), and `r publication_overall$Var1[6]` (`r format(publication_overall$Percent[6], nsmall = 1, digits = 1)`%). We will include all information over 1% of the publication totals.

```{r echo = FALSE}
o_total_output <- tidy(o_total_model)
var_o_total_output <- tidy(var_o_total_model)

s_total_output <- tidy(s_total_model)
var_s_total_output <- tidy(var_s_total_model)
```

**_Publication Metrics_**. The average number of all publications per individual was *M* = `r format(round(mean(merged_df$o_total_pub, na.rm = T), digits = 2), nsmall = 2)` (*SD* = `r format(round(sd(merged_df$o_total_pub, na.rm = T), digits = 2), nsmall = 2)`) using ORCID and *M* = `r format(round(mean(merged_df$s_total_pub, na.rm = T), digits = 2), nsmall = 2)` (*SD* = `r format(round(sd(merged_df$s_total_pub, na.rm = T), digits = 2), nsmall = 2)`) using Google Scholar. The average i10 index was *M* = `r format(round(mean(merged_df$i10_index, na.rm = T), digits = 2), nsmall = 2)` (*SD* = `r format(round(sd(merged_df$i10_index, na.rm = T), digits = 2), nsmall = 2)`) and the average h-index was *M* = `r format(round(mean(merged_df$h_index, na.rm = T), digits = 2), nsmall = 2)` (*SD* = `r format(round(sd(merged_df$h_index, na.rm = T), digits = 2), nsmall = 2)`).

Using the same analyses as career length, we will report:

1) Number of publications ORCID:

  - The slope for number of publications was *b* = `r format(round(o_total_output$estimate[2], digits = 2), nsmall = 2)`, *SE* = `r format(round(o_total_output$std.error[2], digits = 2), nsmall = 2)`, *t*(`r o_total_output$df[2]`) = `r format(round(o_total_output$statistic[2], digits = 2), nsmall = 2)`, *p* = `r printp(o_total_output$p.value[2])`. 
  - The variance parameter was *SD* = `r format(round(o_total_output$estimate[3], digits = 2), nsmall = 2)`. 
  - The slope for variance across years was *b* = `r format(round(var_o_total_output$estimate[2], digits = 2), nsmall = 2)`, *SE* = `r format(round(var_o_total_output$std.error[2], digits = 2), nsmall = 2)`, *t*(`r var_o_total_model$df.residual`) = `r format(round(var_o_total_output$statistic[2], digits = 2), nsmall = 2)`, *p* = `r printp(var_o_total_output$p.value[2])`.

2) The number of publications for Scholar:

  - The slope for year of first publication was *b* = `r format(round(s_total_output$estimate[2], digits = 2), nsmall = 2)`, *SE* = `r format(round(s_total_output$std.error[2], digits = 2), nsmall = 2)`, *t*(`r s_total_output$df[2]`) = `r format(round(s_total_output$statistic[2], digits = 2), nsmall = 2)`, *p* = `r printp(s_total_output$p.value[2])`. 
  - The variance parameter was *SD* = `r format(round(s_total_output$estimate[3], digits = 2), nsmall = 2)`. 
  - The slope for variance across years was *b* = `r format(round(var_s_total_output$estimate[2], digits = 2), nsmall = 2)`, *SE* = `r format(round(var_s_total_output$std.error[2], digits = 2), nsmall = 2)`, *t*(`r var_s_total_model$df.residual`) = `r format(round(var_s_total_output$statistic[2], digits = 2), nsmall = 2)`, *p* = `r printp(var_s_total_output$p.value[2])`.

@@

Discuss the limitation of "who is using ORCID and Scholar" which is likely biasing our results.

### 2022-06-03 04.manuscript.tex
pushing old updates

\textbf{\emph{Types of Publications}}.
- print out overall
- print out over time
- open science question

\textbf{\emph{Publication Metrics}}.
- means and SDs for i10 and hindex information, and number of publications
- same analyses as career length - slope of number of publications and variance of number of publications
- slope up means people who are publishing more are more represented in the researchers
- slope down means more people with less publications
- answer are we giving opportunities to people who need the bean counting

@@

\textbf{\emph{Types of Publications}}.
- print out overall
- print out over time
- open science question

\textbf{\emph{Publication Metrics}}.
- means and SDs for i10 and hindex information, and number of publications
- same analyses as career length - slope of number of publications and variance of number of publications
- slope up means people who are publishing more are more represented in the researchers
- slope down means more people with less publications
- answer are we giving opportunities to people who need the bean counting

@@

>>>>

\textbf{\emph{Types of Publications}}. We will summarize the coded types of publications for individuals.

\textbf{\emph{Publication Metrics}}. We will report descriptive statistics on the total number of publications, i10 index, and h-index for individuals overall. Next, we will use the same analyses described in the career length section to analyze trends over time. An increasing slope over time indicates that individuals who are publishing more are more represented in big-team science over time (i.e., increasing numbers of scholars with higher publication rates), while a negative slope indicates more researchers with less publications. A positive slope for variance indicates increasing variance over time (i.e., more diversity in the individual publication rates), while a negative slope would indicate less diversity in researchers over time. While publication rates do not represent value as a researcher, they are often used in hiring and promotion decisions, and we will use this variable as a proxy to gauge the diversity in scholars represented in big teams.

@@

\textbf{\emph{Types of Publications}}. In general, the most common type of publication was journal-article (78.7\%), followed by other (7.7\%), and smaller categories for conference (5.4\%), book (5.1\%), preprint (1.3\%), and software (0.7\%). We will include all information over 1\% of the publication totals.

\textbf{\emph{Publication Metrics}}. The average number of all publications per individual was \emph{M} = 52.69 (\emph{SD} = 70.37) using ORCID and \emph{M} = 64.20 (\emph{SD} = 110.06) using Google Scholar. The average i10 index was \emph{M} = 30.96 (\emph{SD} = 56.44) and the average h-index was \emph{M} = 18.55 (\emph{SD} = 21.89).

Using the same analyses as career length, we will report:

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  Number of publications ORCID:
\end{enumerate}

\begin{itemize}
\tightlist
\item
  The slope for number of publications was \emph{b} = -0.02, \emph{SE} = 2.02, \emph{t}(22) = -0.01, \emph{p} = .991.
\item
  The variance parameter was \emph{SD} = 29.13.
\item
  The slope for variance across years was \emph{b} = 1.94, \emph{SE} = 5.44, \emph{t}(23) = 0.36, \emph{p} = .725.
\end{itemize}

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\setcounter{enumi}{1}
\tightlist
\item
  The number of publications for Scholar:
\end{enumerate}

\begin{itemize}
\tightlist
\item
  The slope for year of first publication was \emph{b} = 0.00, \emph{SE} = 0.00, \emph{t}(15) = 1.68, \emph{p} = .114.
\item
  The variance parameter was \emph{SD} = 100.62.
\item
  The slope for variance across years was \emph{b} = -38.52, \emph{SE} = 6.27, \emph{t}(2) = -6.14, \emph{p} = .026.
\end{itemize}

@@

Discuss the limitation of ``who is using ORCID and Scholar'' which is likely biasing our results.
